---
title: "Quality report for MRI"
output: word_document
---

```{r,include=FALSE}
#load("bp.rdata")       # example data
source("RLS_MRI_QC_v1.R")  # standard qa functions
MRIvisitreport <- RsPrepareQa(MRIvisitreport)
MRIcontrareport <- RsPrepareQa(MRIcontrareport)
#cardioData <- RsPrepareQa(cardioData)
library(knitr)
options(encoding = 'UTF-8')
```

This is the QA report for MRI. 
This report was generated on the `r format(Sys.Date(), '%d. %B %Y')`.


### Completeness of Contra-indications datasets

The following table shows the number of Contra-Indications Interviews as indicated by
the status "OK" given by the MRI techniciant.

```{r, echo=FALSE}
kable(RsStatusByDate(MRIcontrareport) %>%
        rename(Month=metadata_exam_date_group),
      caption="Number of participants per month")
```

### Completeness of MRI datasets

The following table shows the number of MRI datasets as indicated by
the status "OK" given by the MRI techniciant.

```{r, echo=FALSE}
kable(RsStatusByDate(MRIvisitreport) %>%
        rename(Month=metadata_exam_date_group),
      caption="Number of participants per month")
```

The following chart shows the same, split by the various possible states of the examinations.

```{r, echo=FALSE}
MRIvisitreport %>% 
  group_by(metadata_exam_date_group, metadata_exam_status) %>%
  summarize(N = n()) %>%

ggplot(aes(x=metadata_exam_date_group, y=N,
           group=metadata_exam_status)) +
			 geom_bar(aes(fill=metadata_exam_status), stat="identity") +
  theme(legend.position="top") +
	theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  xlab("month")+ylab("N")+
  ggtitle("Number of datasets per month, by status")+
  labs(fill="Status")+
  guides(fill=guide_legend(nrow=2))+
  scale_fill_hue(limits = c("CONTRA", "SKIPPED", "OK", "NOT_UPLOADED_YET", "TIMEOUT", "INCOMPLETE", "INCOMPLETE_TIMEOUT", "INCOMPLETE_TECHNICAL"), labels=c("CI/Exclusion", "Skipped", "OK", "Not uploaded yet", "Not done_timeout", "Incomplete", "Incomplete_timeout", "Incomplete_technical issue"))
```

### Duration of the Contra-indications interview

The following table shows the median and p90 duration in min of the
examination "Contra-indications interview" per age group.

```{r, echo=FALSE}
kable(RsDurationByAge(MRIcontrareport) %>%
        rename(Age_group=metadata_pt_age_group),
      caption="Duration by age group")
```

The following figure shows boxplots of the duration of the examination
"Contra-indications interview" which were marked "OK" per age group.

```{r, echo=FALSE}
# depending on the examination, maybe filter by state before plotting
plannedCutoff <- 10
MRIcontrareport %>% filter(metadata_exam_status == 'OK') %>% 
  filter(!is.na(metadata_exam_duration_min)) %>% 
ggplot(aes(x=metadata_pt_age_group, y=metadata_exam_duration_min))+
  stat_boxplot(geom="errorbar", width = 0.5)+
  geom_hline(yintercept=plannedCutoff,linetype="dashed",colour="red")+
  geom_boxplot()+
  xlab("age group")+ylab("duration of examination [min]")+
  ggtitle("Contra-indications measurement\nduration per age group")
```


## MRI contraindication interview

table with results from the interview
```{r, echo=FALSE}
MRIcontrareport %>% group_by(metadata_exam_date_group) %>% 
  summarize(N=n(), operation = sum(mrici_op=="YES", na.rm=TRUE),
            surgery = sum(mrici_implant=="YES", na.rm=TRUE),
            metalinplant = sum(mrici_metal=="YES", na.rm=TRUE),
            tatoo = sum(mrici_tatoo=="YES", na.rm=TRUE),
            metalwork = sum(mrici_metalwork=="YES", na.rm=TRUE),	
            bling = sum(mrici_bling=="YES", na.rm=TRUE),
            seizure = sum(mrici_seizure=="YES", na.rm=TRUE),	
            pregnant = sum(mrici_pregnant=="YES", na.rm=TRUE)) %>%
  kable()
```


## Comparisons with other examinations

```{r, include=FALSE}
allComplete <- RsComplete(MRIvisitreport, MRIcontrareport) #WH can add more "report - basicly a merge"
```


